---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/",
  out.width = "100%"
)
```



## :mortar_board: Practice 1 - Research Compendium


<!-- badges: start -->
[![License: GPL-2](https://img.shields.io/badge/License-GPL%20v2-blue.svg)](https://choosealicense.com/licenses/gpl-2.0/)
[![Website](https://github.com/rdatatoolbox/practice1/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/rdatatoolbox/practice1/actions/workflows/pkgdown.yaml)
<!-- badges: end -->


Structure of the research compendium of the [practice 1](https://rdatatoolbox.github.io/ex-compendium.html) of the training course 
[**Reproducible Research in Computational Ecology**](https://rdatatoolbox.github.io).



### Content

This repository is structured as follow:

- [`data/`](https://github.com/rdatatoolbox/practice1/tree/main/data):
contains all raw data required to perform analyses

- [`analyses/`](https://github.com/rdatatoolbox/practice1/tree/main/analyses/):
contains R scripts to run each step of the workflow

- [`R/`](https://github.com/rdatatoolbox/practice1/tree/main/R):
contains R functions developed especially for this project

- [`DESCRIPTION`](https://github.com/rdatatoolbox/practice1/tree/main/DESCRIPTION):
contains project metadata (author, date, dependencies, etc.)

- [`make.R`](https://github.com/rdatatoolbox/practice1/tree/main/make.R):
main R script to run the entire project by calling each R script stored in the `analyses/` folder



### Usage

Fork and clone the repository, open R/RStudio and run:

```{r eval=FALSE}
source("make.R")
```



### Notes

- All required packages, listed in the `DESCRIPTION` file, will be installed (if necessary)
- All required packages and R functions will be loaded



### How to cite

> Casajus N, Bonnici I, Dray S, Gimenez O, Guéry L, Guilhaumon F, Schiettekatte NMD & Siberchicot A (2023) Workshop FRB-CESAB & RT EcoStat: Reproducible Research in Computational Ecology. Zenodo. <http://doi.org/10.5281/zenodo.4262978>.
